analysis

### 2021-11-12 code/analysis_code/analysisscript.Rmd
Referencing Completed!

#get a table
```{r}
overall_summary <- table1(~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure   , data=mydata, overall="Total")
overall_summary
```
```{r}
df100 = data.frame(overall_summary)
summarytable_file = here("results", "Overall.rds")
saveRDS(df100, file = summarytable_file)
```

@@

#resampling method
```{r}
set.seed(200)
mydata_folds <- vfold_cv(mydata, v = 10)
```

>>>>

#get a table
```{r}
overall_summary <- table1(~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure   , data=mydata, overall="Total")
overall_summary
```

```{r}
df100 = data.frame(overall_summary)
summarytable_file = here("results", "Overall.rds")
saveRDS(df100, file = summarytable_file)
```

@@

# Put 70% of the data into the training set and 30% into testing using strata=BodyTemp
```{r}
data_split <- initial_split(mydata, prop = 0.7, strata = infection_status_info)
```

# Create data frames for the two sets:
```{r}
train_data <- training(data_split)
test_data  <- testing(data_split)
```

# training set proportions by class
```{r}
train_data %>% 
  count(infection_status_info) %>% 
  mutate(prop = n/sum(n))
```

# test set proportions by class
```{r}
test_data %>% 
  count(infection_status_info) %>% 
  mutate(prop = n/sum(n))
```
##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds
```{r}
mydata_folds <- vfold_cv(train_data, v = 5, repeats =5, strata= "infection_status_info")
```
